**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study.

### 2017-05-24 doc/adaAbstract.Rmd
gee plot

```{r}
gee3 <- readRDS(file = "../data/ds.Rds") %>%
  dplyr::mutate(
  udbpBase = ifelse(fVN == "Baseline", UDBP, NA),
  ageBase = ifelse(fVN == "Baseline", Age, NA),
  VitaminD3 = ifelse(fVN == "6Year", NA, VitaminD)
  # Ethnicity = ifelse(Ethnicity == "European", Ethnicity, "Other"),
  ) %>%
  dplyr::arrange(SID, fVN) %>%
  dplyr::group_by(SID) %>%
  tidyr::fill(udbpBase, ageBase) %>%
  dplyr::ungroup() %>%
  # dplyr::group_by(VN) %>%
  # dplyr::mutate(udbpBase = as.numeric(scale(udbpBase))) %>%
  dplyr::mutate(UDBP = UDBP/1000) %>%
  # dplyr::ungroup() %>% 
  dplyr::arrange(SID, VN) %>%
  mason_gee(
  yvars = c("VitaminD3"),
  xvars = "UDBP",
  covars = c("VN", "ageBase", "DM")
  )
```

>>>>

```{r gee plot}

gee %>% 
  dplyr::mutate(Xterms = term) %>% 
  dplyr::filter(!term == "(Intercept)") %>% 
  dplyr::mutate(Yterms = factor(Yterms, 
                                levels = c("ACR", "eGFR"),
                                ordered = TRUE),
                Xterms = factor(Xterms,
                                levels = rev(c("<-Xterm",
                                           "VN",
                                           "ageBase",
                                           "SexMale",
                                           "EthnicityEuropean",
                                           "BMI",
                                           "fDMdiabetes")),
                                labels = rev(c("uVDBP",
                                           "Follow-up Duration",
                                           "Baseline Age",
                                           "Sex (male)",
                                           "Ethnicity (European)",
                                           "BMI",
                                           "Diabetes")),
                                ordered = TRUE)) %>% 
  arrange(Xterms) %>% 
  gee_plot(xlab = "Unit change for every unit increase in uVDBP")
```
